%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% filename    : sp.tex
% author      : Karl Frederick Roldan, Gerd Lowell Jana, John Kenneth Lesaba
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% BUGFIX: Save LaTeX kernel version of \@xfloat
\makeatletter
\let\my@xfloat\@xfloat
\makeatother

% use ateneo de naga etd class (actually modified virginia tech's etd class)
\documentclass[oneside]{etd}

% BUGFIX: Create a modified copy of \@xfloat using the kernel definition
\makeatletter
\def\@xfloat#1[#2]{
	\my@xfloat#1[#2]%
	\def\baselinestretch{1}%
	\@normalsize \normalsize
}
\makeatother

% use these packages

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{latexsym}
\usepackage{amsmath}
%\usepackage[lineno5,noindent]{lgrind}
%\usepackage{rotating} 
%\usepackage{makeidx}
%\usepackage{stmaryrd}
\usepackage{float}
\usepackage{subfigure}
%\usepackage{cite}
%\usepackage{moreverb}
%\usepackage{pictexwd,dcpic}
\usepackage{algorithm,algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{tikz}
\usetikzlibrary{positioning,calc}

\usepackage{listings}
\definecolor{cppred}{rgb}{0.6,0,0} % for strings
\definecolor{cppgreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{cpppurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{cppdocblue}{rgb}{0.25,0.35,0.75} % doc
 
\lstset{language=C++,
basicstyle=\linespread{0.8}\ttfamily\small,
keywordstyle=\color{cpppurple}\bfseries,
stringstyle=\color{cppred},
commentstyle=\color{cppgreen},
morecomment=[s][\color{cppdocblue}]{/**}{*/},
numbers=left,
numberstyle=\tiny\color{black},
% stepnumber=2,
numbersep=10pt,
tabsize=4,
showspaces=false,
showstringspaces=false}

\graphicspath{{figures/}{./}}

%\renewcommand{\floatpagefraction}{0.8}

\makeindex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Multiclass classification via Transformer Networks for Task Constraint-based Introductory Programming Feedback}
\author{My Name}
\department{Computer Science}
\BSdegree
\field{Computer Science}
\degreemonth{May}  % date of final defense
\degreeyear{2022}

\threestudents
{Gerd Lowell Jana}
{John Kenneth Lesaba}
{Karl Frederick Roldan}

\threestudentsheader
{Jana, Lesaba, and Roldan}

\threedegrees
{Computer Science}
{Computer Science}
{Computer Science}


\advisor
{Joshua C. Martinez, MIT}
\threemembers
{Raphael Henry M. Garay}
{Glenn G. Fabia}
{John Sixto G. Santos, MS}
\deanandchair
{Joshua C. Martinez, MIT}
{Adrian Leo Pajarillo, MS}

\keywords{CS Education, transformer}


\begin{document}

\maketitle
\makerecomm
\makeacceptance
\makedeclaration

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    ABSTRACT/EXECUTIVE SUMMARY                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%execsummary
\begin{abstract}
	Task constraint feedback is a kind of feedback that checks whether problem-defined 
	constraints were fulfilled by students upon submission of work. The feedback process 
	can be as simple as checking if a certain programming construct exists or if the 
	student used a specific algorithm or data structure as prescribed by the problem. 
	Most task constraint systems, such as \textit{WeBWoRK-JAG} and \textit{Fischer06}, use basic static 
	analysis and comprehensive automated testing. ProPL, a task constraint checker, is 
	an exemption which uses natural language processing techniques to generate feedback. 
	In this study, the proponents will use Transformer Networks which have been known to 
	work really well with sequence-to-sequence natural language models such as neural 
	translation, text generation, and summarization. Previous works showed evidence 
	that transformer networks can be generalized for use in programming language processing 
	such as code generation. The study will apply transformer networks to generate classes 
	that are used in the submitted codes of students to generate relevant task constraint 
	feedback. This study aims to show how transformers can be applied in aiding computer 
	science education through task-constraint feedback.
\end{abstract}

	
\include{misc/dedication}
\include{misc/acknowledgements}

\begingroup
\renewcommand*{\addvspace}[1]{}
\tableofcontents
% \listoffigures
% \listoftables
\endgroup

\beginbody
\pagenumbering{arabic}

\include{chapters/introduction}
\include{chapters/review}
\include{chapters/techbackground}
\include{chapters/methodology}
% \include{chapters/results}
% \include{chapters/recommendations}

\appendix
\include{appendices/researchtimeline}
% \include{appendices/evaltool}
% \include{appendices/reports}
% \include{appendices/io}
% \include{appendices/code}
% \include{appendices/usersguide}

\nocite{*}
\bibliographystyle{siam}
\bibliography{sources.bib}



% \include{misc/vita}

\end{document}
